---
title: "Admixture Graphs"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/emilydittmar/Google Drive/Active Projects/DelMutation/Data/Preliminary_Aug2020")
```

# Import/sort metadata
```{r metadata, echo=FALSE}

# Line Order is list of filenames that went into ANGSD as input
LineOrder <- read.table("Subset1_BamRealigned.txt", sep = "/")
LineOrder$V7 <- gsub("_realigned.bam", "", LineOrder$V7)

# read in Metadata
meta <- read.csv("DomesticatedSubset_Metadata.csv", header=T)
aggregate(meta$PPN, by=list(meta$type2), length)
# re-order factor levels
meta$type2 <- factor(meta$type2, levels=c("INRA-HA", "INRA-RHA", "HA-NonOil", "HA-Oil", "RHA-Oil", "RHA-NonOil", "introgressed-NonOil", "landrace", "OPV-NonOil", "other-NonOil", "other-Oil"))
meta$het_group <- factor(meta$het_group, levels=c("HA", "RHA", "other", "landrace"))

```


## Function to format data for graphing
```{r function, echo=FALSE}

AdmixGraph <- function (admixdf, LineOrderDf, MetaData, sortFactor) {
  admix_data <- cbind.data.frame(LineOrderDf, admixdf)
  colnames(admix_data)[1] <- "PPN"
  allAdmix <- merge(MetaData, admix_data, by = "PPN")
  allAdmix_sort <- allAdmix[order(allAdmix[[sortFactor]]),]
  lengths <- aggregate(allAdmix_sort$PPN, by=list(allAdmix_sort[[sortFactor]]), length)
  lengths$cum <- cumsum(lengths$x)
  Col1 <- length(MetaData) + 1
  Colx <- length(allAdmix_sort)
  admix <- t(as.matrix(allAdmix_sort[,c(Col1:Colx)]))
  result <- list("admix" = admix, "length" = lengths)
  #result <- list(c(admix, lengths), names=c("admixturedf", "lengths"))
  return(result)
}

AdmixPlot <- function (MatrixData, GroupLengthVector) {
  barplot(MatrixData, col=c("#006BA4","#FF800E","#A2C8EC",
                     "#898989","#ABABAB","#595959",
                     "#5F9ED1","#CFCFCF","#FFBC79","#C85200"),
        space = 0,
        border = NA,
        #xlab = "Individuals",
        ylab = "Admixture proportion")
abline(v=c(GroupLengthVector), lwd=2)
}

# combined
AdmixDataPlot <- function(filename, LineOrderDf, MetaData, sortFactor){
  data <- read.table(filename)
  graphdata <- AdmixGraph(data, LineOrderDf, MetaData, sortFactor)
  AdmixPlot(graphdata$admix, graphdata$length$cum)
}
```

## Two Groups
```{r Admix2, echo=FALSE}

admix2 <- read.table("Cultivated_GenomeSubset.2.qopt.graph.me")

admix2_graph <- AdmixGraph(admix2, LineOrder$V7, meta[,c(2,6,8:11)], "type2")

barplot(admix2_graph$admix, col=c("#006BA4","#FF800E","#A2C8EC",
                     "#898989","#ABABAB","#595959",
                     "#5F9ED1","#CFCFCF","#FFBC79","#C85200"),
        space = 0,
        border = NA,
        #xlab = "Individuals",
        ylab = "Admixture proportion")
abline(v=c(admix2_graph$length$cum), lwd=2)

AdmixPlot(admix2_graph$admix, admix2_graph$length$cum)

```


## Three Groups
```{r Admix3, echo=FALSE}

admix3 <- read.table("Cultivated_GenomeSubset.3.qopt.graph.me")

admix3_graph <- AdmixGraph(admix3, LineOrder$V7, meta[,c(2,6,8:11)], "type2")

barplot(admix3_graph$admix, col=c("#006BA4","#FF800E","#A2C8EC",
                     "#898989","#ABABAB","#595959",
                     "#5F9ED1","#CFCFCF","#FFBC79","#C85200"),
        space = 0,
        border = NA,
        #xlab = "Individuals",
        ylab = "Admixture proportion")
abline(v=c(admix3_graph$length$cum), lwd=2)

AdmixPlot(admix3_graph$admix, admix3_graph$length$cum)

```

## Four Groups
```{r Admix4, echo=FALSE}

AdmixDataPlot("Cultivated_GenomeSubset.2.qopt.graph.me", LineOrder$V7, meta[,c(2,6,8:11)], "type2")

AdmixDataPlot("Cultivated_GenomeSubset.3.qopt.graph.me", LineOrder$V7, meta[,c(2,6,8:11)], "type2")

AdmixDataPlot("Cultivated_GenomeSubset.4.qopt.graph.me", LineOrder$V7, meta[,c(2,6,8:11)], "type2")

AdmixDataPlot("Cultivated_GenomeSubset.5.qopt.graph.me", LineOrder$V7, meta[,c(2,6,8:11)], "type2")